RSA_model2

### 2015-10-26 models/RSA_Model2.Rmd
adjustments for Symsys 290 preso 10.26.15

Run model
---------
```{r}
alpha = 1
md <- data %>%
  do(run.rsa(., alpha = alpha, useprior = T, usenone = T))
```

Visualize
---------
```{r}
qplot(stars, listener.p, col=degree, 
      data=md,
      main=paste("Model vs Human judgments\nSemantics measured empirically\nalpha=",
                 alpha),
      ylab="Posteriors p( rating | word )") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

ggplot(md, aes(x=pred, y=listener.p)) +
    geom_point(aes(colour = stars)) +
    geom_smooth(method=lm) +
  ggtitle("Model performance\nCorpus based") +
  labs(x = "model prediction", y="human judgments")
cor(md$pred, md$listener.p)

# scalar level cor
specific.cor = function(scalar) {
  return (cor(md[which(md$scale==scalar), ]$pred,
              md[which(md$scale==scalar), ]$listener.p))
}
qplot(unique(md$scale), y = sapply(unique(md$scale), specific.cor),
    aes(group=1), geom="bar", stat="identity")
```

@@

>>>>

Run model
---------
```{r}
alpha = 4
md <- data %>%
  do(run.rsa(., alpha = alpha, useprior = T, usenone = T))
```

Visualize
---------
```{r}
qplot(stars, listener.p, col=degree, 
      data=md,
      main=paste("Model vs Human judgments\nSemantics measured empirically\nalpha=",
                 alpha),
      ylab="Posterior p(rating | word)") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

ggplot(md, aes(x=pred, y=listener.p)) +
    geom_point(aes(colour = stars)) +
    geom_smooth(method=lm) +
  ggtitle("Model performance: Baseline") +
  labs(x = "model prediction", y="human judgments")
cor(md$pred, md$listener.p)^2
cor.test(md$pred, md$listener.p)
# scalar level cor
specific.cor = function(scalar) {
  return (cor(md[which(md$scale==scalar), ]$pred,
              md[which(md$scale==scalar), ]$listener.p))
}
qplot(unique(md$scale), y = sapply(unique(md$scale), specific.cor),
    aes(group=1), geom="bar", stat="identity")
```

@@

For Presentation to Symsys290 10.26.15
```{r}
qplot(stars, listener.p, col=degree, 
      data=md[md$scale=="some_all",],
      main=paste("Model vs Human judgments\nalpha=",
                 alpha),
      ylab="Posterior p(m | u)") +
  geom_line(aes(y = pred), lty = 4)
```
